An Algorithm For Spatial Mapping Using a Hexagon Tile Map, With Application to Australian Maps

### 2020-07-20 kobakian_sugarbag_jss/kobakian_sugarbag_jss.tex

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\hypertarget{algorithm}{%
\section{Algorithm}\label{algorithm}}

@@

\hypertarget{parameters}{%
\subsection{Parameters}\label{parameters}}

@@

\hypertarget{polygon-set}{%
\subsection{Polygon set}\label{polygon-set}}

@@

\hypertarget{create-the-set-of-centroid-points}{%
\subsection{Create the set of centroid
points}\label{create-the-set-of-centroid-points}}

@@

\hypertarget{create-the-hexagon-grid-points}{%
\subsection{Create the hexagon grid
points}\label{create-the-hexagon-grid-points}}

@@

\hypertarget{step-1-creating-a-tesselated-grid}{%
\subsubsection{Step 1: Creating a tesselated
grid}\label{step-1-creating-a-tesselated-grid}}

@@

\hypertarget{step-2-rolling-windows}{%
\subsubsection{Step 2: Rolling windows}\label{step-2-rolling-windows}}

@@

\hypertarget{step-3-filtering-the-grid}{%
\subsubsection{Step 3: Filtering the
grid}\label{step-3-filtering-the-grid}}

@@

\hypertarget{centroid-to-focal-point-distance}{%
\subsection{Centroid to focal point
distance}\label{centroid-to-focal-point-distance}}

@@

\hypertarget{allocate-each-centroid-to-a-hexagon-grid-point}{%
\subsection{Allocate each centroid to a hexagon grid
point}\label{allocate-each-centroid-to-a-hexagon-grid-point}}

@@

\begin{CodeInput}
R> hexmap_allocation <- allocate(
R>   centroids = centroids %>% select(SA2_NAME16, longitude, latitude),
R>   sf_id = "SA2_NAME16",
R>   hex_grid = grid,
R>   hex_size = 0.2, # same size used in create_grid
R>   hex_filter = 10,
R>   width = 35,
R>   focal_points = capital_cities,
R>   verbose = TRUE)
\end{CodeInput}
\end{CodeChunk}

@@

\hypertarget{step-1-filter-the-grid-for-unassigned-hexagon-points}{%
\subsubsection{Step 1: Filter the grid for unassigned hexagon
points}\label{step-1-filter-the-grid-for-unassigned-hexagon-points}}

@@

\hypertarget{step-2-filter-the-grid-points-for-those-closest-to-the-centroid}{%
\subsubsection{Step 2: Filter the grid points for those closest to the
centroid}\label{step-2-filter-the-grid-points-for-those-closest-to-the-centroid}}

@@

\hypertarget{neighbour-relationships}{%
\subsection{Neighbour relationships}\label{neighbour-relationships}}

@@

\hypertarget{using-sugarbag}{%
\section{Using sugarbag}\label{using-sugarbag}}

\hypertarget{installation}{%
\subsection{Installation}\label{installation}}

@@

\hypertarget{creating-a-hexagon-tile-map}{%
\subsection{Creating a hexagon tile
map}\label{creating-a-hexagon-tile-map}}

@@

\begin{CodeInput}
R> # Load data
R> data(tas_sa2)
R> 
R> # Create centroids set
R> centroids <- create_centroids(tas_sa2, "SA2_NAME16")
R> 
R> # Create hexagon grid
R> grid <- create_grid(centroids = centroids,
R>     hex_size = 0.2,
R>     buffer_dist = 1.2)
R> 
R> # Allocate polygon centroids to hexagon grid points
R> hex_allocated <- allocate(
R>   centroids = centroids,
R>   hex_grid = grid,
R>   sf_id = "SA2_NAME16",
R>   # same column used in create_centroids
R>   hex_size = 0.2,
R>   # same size used in create_grid
R>   hex_filter = 10,
R>   use_neighbours = tas_sa2,
R>   focal_points = capital_cities %>% filter(points == "Hobart"),
R>   width = 35,
R>   verbose = FALSE)
R> 
R> # Prepare to plot
R> fort_hex <- fortify_hexagon(data = hex_allocated, sf_id = "SA2_NAME16", hex_size = 0.2)
R> 
R> # Make a plot
R> library(ggplot2)
R> ggplot(fort_hex) + 
R>   geom_polygon(aes(x=long, y=lat, group=hex_id, fill = lat)) +
R>   scale_fill_distiller("", palette="PRGn")
\end{CodeInput}
\end{CodeChunk}

\hypertarget{applications}{%
\section{Applications}\label{applications}}

\hypertarget{australian-cancer-atlas}{%
\subsection{Australian Cancer Atlas}\label{australian-cancer-atlas}}

@@

\hypertarget{animation}{%
\section{Animation}\label{animation}}

@@

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

@@

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

>>>>

\hypertarget{introduction}{%
\subsection{Introduction}\label{introduction}}

@@

\hypertarget{algorithm}{%
\subsection{Algorithm}\label{algorithm}}

@@

\hypertarget{parameters}{%
\paragraph{Parameters}\label{parameters}}

@@

\hypertarget{polygon-set}{%
\paragraph{Polygon set}\label{polygon-set}}

@@

\hypertarget{create-the-set-of-centroid-points}{%
\paragraph{Create the set of centroid
points}\label{create-the-set-of-centroid-points}}

@@

\hypertarget{create-the-hexagon-grid-points}{%
\paragraph{Create the hexagon grid
points}\label{create-the-hexagon-grid-points}}

@@

Step 1: Creating a tesselated grid

@@

Step 2: Rolling windows

@@

Step 3: Filtering the grid

@@

\hypertarget{centroid-to-focal-point-distance}{%
\paragraph{Centroid to focal point
distance}\label{centroid-to-focal-point-distance}}

@@

\hypertarget{allocate-each-centroid-to-a-hexagon-grid-point}{%
\paragraph{Allocate each centroid to a hexagon grid
point}\label{allocate-each-centroid-to-a-hexagon-grid-point}}

@@

\begin{CodeInput}
R> hexmap_allocation <- allocate(
R>   centroids = centroids %>% select(SA2_NAME16, longitude, latitude),
R>   sf_id = "SA2_NAME16",
R>   hex_grid = grid,
R>   hex_size = 0.2, ## same size used in create_grid
R>   hex_filter = 10,
R>   width = 35,
R>   focal_points = capital_cities,
R>   verbose = TRUE)
\end{CodeInput}
\end{CodeChunk}

@@

Step 1: Filter the grid for unassigned hexagon points

@@

Step 2: Filter the grid points for those closest to the centroid

@@

\hypertarget{neighbour-relationships}{%
\paragraph{Neighbour relationships}\label{neighbour-relationships}}

@@

\hypertarget{using-sugarbag}{%
\subsection{Using sugarbag}\label{using-sugarbag}}

\hypertarget{installation}{%
\paragraph{Installation}\label{installation}}

@@

\hypertarget{creating-a-hexagon-tile-map}{%
\paragraph{Creating a hexagon tile
map}\label{creating-a-hexagon-tile-map}}

@@

\begin{CodeInput}
R> ## Load data
R> data(tas_sa2)
R> 
R> ## Create centroids set
R> centroids <- create_centroids(tas_sa2, "SA2_NAME16")
R> 
R> ## Create hexagon grid
R> grid <- create_grid(centroids = centroids,
R>     hex_size = 0.2,
R>     buffer_dist = 1.2)
R> 
R> ## Allocate polygon centroids to hexagon grid points
R> hex_allocated <- allocate(
R>   centroids = centroids,
R>   hex_grid = grid,
R>   sf_id = "SA2_NAME16",
R>   ## same column used in create_centroids
R>   hex_size = 0.2,
R>   ## same size used in create_grid
R>   hex_filter = 10,
R>   use_neighbours = tas_sa2,
R>   focal_points = capital_cities %>% filter(points == "Hobart"),
R>   width = 35,
R>   verbose = FALSE)
R> 
R> ## Prepare to plot
R> fort_hex <- fortify_hexagon(data = hex_allocated, sf_id = "SA2_NAME16", hex_size = 0.2)
R> 
R> ## Make a plot
R> library(ggplot2)
R> ggplot(fort_hex) + 
R>   geom_polygon(aes(x=long, y=lat, group=hex_id, fill = lat)) +
R>   scale_fill_distiller("", palette="PRGn")
\end{CodeInput}
\end{CodeChunk}

\hypertarget{applications}{%
\subsection{Applications}\label{applications}}

\hypertarget{australian-cancer-atlas}{%
\paragraph{Australian Cancer Atlas}\label{australian-cancer-atlas}}

@@

\hypertarget{animation}{%
\subsection{Animation}\label{animation}}

@@

\hypertarget{conclusion}{%
\subsection{Conclusion}\label{conclusion}}

@@

\hypertarget{acknowledgements}{%
\subsection{Acknowledgements}\label{acknowledgements}}
